A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-23 text/properties.tex
Fix the proof of Inversion Lemma for $\Pi$ type.
Revise the proof of Inversion Lemma for $\TW$ type.

\begin{lemma}[Inversion]\ 
  \begin{enumerate}
  \item If $\G \V (\lambda x:\sigma.M) : (\Pi x:\sigma'.\tau)@A$,
    then $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma@A\V M:\tau @A$.
  \item If $\G \V \TB_\alpha M : \TW_\alpha \tau @A$ then $\G \V M : \tau @A$.
  \item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
  \end{enumerate}
\end{lemma}

@@

Strong Normalization is also an important property, which guarantees that
no typed term has an infinite reduction sequence.
We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{harper1993framework}.
\AI{what is a standard citation for a proof of SN of a dependently typed calculus?}.
\red{とりあえずA Framework for Defining Logicsを引用しました。}

>>>>

\begin{lemma}[Inversion]\ 
	\begin{enumerate}
		\item If $\G \V (\lambda x:\sigma.M) : \rho$ then there are $\sigma'$ and $\tau'$ such that
		      $\rho = \Pi x:\sigma'.\tau'$, $\G \V \sigma \E \sigma'@A$ and $\G ,x:\sigma'@A\V M:\tau'@A$.
		\item If $\G \V \TB_\alpha M : \tau@A$ then 
		      there is $\sigma$ such that $\tau = \TW_\alpha \sigma$ and $\G \V M : \sigma@A$.
		\item If $\G \V \Lambda\alpha.M : \forall\alpha.\tau @A$ then $\G \V M : \tau @A$ and $\alpha \notin \FTV(\G) \cup \FV(A)$.
	\end{enumerate}
\end{lemma}

@@

Strong Normalization is also an important property, which guarantees that
no typed term has an infinite reduction sequence.
We prove this thorem by translating \LMD to the symply typed lambda calculus~\cite{harper1993framework}.
